# Version Control in Action

This practical is designed to give you some practice in creating branches, pushing commits and all things Git with the RStudio Git interface!

## Creating and switching between branches

1. Enter the `jrgitpractice` project that we have stored locally upon cloning from our remote repository

2. Have a look at what branches you currently have locally and remotely. What do you think origin means?
   ```{r, tidy=TRUE,                                   tidy.opts=list(width.cutoff=50)}
   # origin is the general word used to describe the
   # upstream remote repository that has been synced
   # with your local copy
   ```

3. Try creating a new branch called dev. Why is it important that we keep the box next to "Sync branch with renote" ticked? 
   ```{r, tidy=TRUE,                                   tidy.opts=list(width.cutoff=50)}
   # This forces the upstream dev remote branch to
   # be formed under the same name as your local
   # branch
   ```

4. As things stand, is there any difference between the files in your master and dev branch? Hint: We can check this by inspecting the Git tab in our dev branch
   ```{r, tidy=TRUE,                                   tidy.opts=list(width.cutoff=50)}
   # No - we have not yet made any changes or added
   # any files to the files already nested within
   # the dev branch. We can see this visually by
   # observing the fact that there are no files
   # ready to be staged for a commit. 
   ```

## Making changes locally and remotely

1. Staying in your dev branch, edit the `hello_myname.R` file by changing "Unknown" to your name. Save it within the `jrgitpractice/` directory. 
2. Tick the box to the left of your filename. What are we doing here and why does an "M" symbol appear?
   ```{r, tidy=TRUE,                                   tidy.opts=list(width.cutoff=50)}
   # We are staging the file in preperation for it
   # to be commited. The M symbol stands for
   # "Modified". This is telling is that we have
   # changed a file that is already stored in the
   # project.
   ```

3. Commit the `hello_myname.R` file. In doing so, provide a short message describing what commit you have made. Why is this important when working on collaborative projects?
   ```{r, tidy=TRUE,                                   tidy.opts=list(width.cutoff=50)}
   # Commit messages are important when working
   # collaboratively because it gives collaborators
   # a clear understanding of the updates you have
   # made to a project. It also serves as a reminder
   # to yourself for future reference.
   ```

4. Switch to your master branch. Why are there no commited files?
   ```{r, tidy=TRUE,                                   tidy.opts=list(width.cutoff=50)}
   # We have made commit objects in our other/dev
   # branch, which is independent of our master
   # branch
   ```

5. Switch back to your dev branch. Push your changes to the remote repository. What branch will be created in the remote repository?
   ```{r, tidy=TRUE,                                   tidy.opts=list(width.cutoff=50)}
   # A branch with the same name (dev) as your new
   # branch will have been created in the remote
   # repository. This is because we kept the box
   # next to "Sync branch with remote" ticked.
   ```

```{r, eval= FALSE, echo = TRUE}
vignette("solutions2", package = "jrGit4u")
```
